---
title: "My First Report"
author: "Josh Mardik"
format:
  html:
    embed-resources: true
---

## Welcome to your practice report

This is a **Quarto** document. It mixes ordinary writing with live code, so your
report and your analysis always stay in sync. When you click **Render**, Quarto
runs the code below and builds a finished HTML page.

Try it now: change `author: "Your Name"` in the header above to your own name,
then click **Render**.

## A first look at the data

The code chunk below reads a small practice dataset from the `data/` folder and
shows the first few rows.

```{r}
patients <- read.csv("data/patients.csv")
head(patients)
```

## A first chart

```{r}
hist(patients$age,
     main = "Age distribution of practice patients",
     xlab = "Age (years)",
     col  = "steelblue")
```

## Your turn

- Add a sentence here describing what you notice in the chart.
-The frequency is at its maximum from ages 40 to 70

- Render again and check that both your sentence and the chart appear.

When you are happy with the result, **commit and sync** your work (the Week 2
course page walks you through this), then submit your repository link on Canvas.



## My Note
I learned how to change document types with in codespace. Along side this we were taught the difference between saving in cloud versus commiting a document for publishing

```{r}
# Code Chunk
3 + 3
```

## Reflection
-Easiest: Changing file types from Quatro to all others
-Confusing: The differences between saving and commiting
-Questions: None at the moment 